Validating FF-Replan vs. a state-of-the-art propabilistic planner in a real world domain

### 2014-03-28 FinalPaper/paper.tex
added initial part domain, summary of domain paper

%
\authorrunning{Paper Plan Seminar Algorithms FF-replan \& RFF}
% (feature abused for this document to repeat the title also on left hand pages)

@@

@@

@@

\begin{itemize}
	\item \cite{Hoffmann01theff}
	\item \cite{FFReplan}
	\item \cite{teichteil2010incremental}
	\item \cite{yoon2008probabilistic}
	\item \cite{teichteil2012fast}
	\item \cite{bonet2011planning}
	\item \cite{taig2013translation}
	\item \cite{martin2013progressive}
	\item \cite{taig2013conformant}
	\item \cite{2013workshop}
	\item \cite{nebel2013much}
	\item \cite{little2007probvsreplan}
	\item \cite{keller2012prost}
	\item \cite{kolobov2012glutton}
\end{itemize}

>>>>

%
\authorrunning{Validating planners in a real world domain}
% (feature abused for this document to repeat the title also on left hand pages)

@@

\subsection{Probabilistic planning}

\subsection{Replanning}
\begin{itemize}
	\item Describe the determinization, or explain
\end{itemize}

@@

\subsubsection{Probabilistic planning vs Replanning}
Inspired by the FF-Replan entrance in the IPPC competition, this paper described a probabilistic interestingness quality of domains. It then compares probabilitsic planners with replanners in the different domains to draw conclusions. Classical planning with replanning upon failure when there is so little or so much uncertainty about the world that it is not worth modelling and reasoning about or when goals dynamically change or when the problem is too large to solve at once. Probabilistic planners are more appropriate when avoiding irreparable or costly failures. Probabilistic planning computes a plan that can handle all foreseeable contingencies and is preferable for quick reactions in closed control loops.

The following structural properties are identified for comparing probabilistic planning with replanning:
\begin{itemize}
	\item 'dead' end states
	\item the degree to which the probability of reaching a deaad end state can be reduced through choice of actions
	\item number of distinct trajectories
	\item presence of mutual exclusion
\end{itemize}

If there are no dead ends, a replanner will always succeed. It is impossible to improve on the unavoidable dead ends (positive probability of reaching when executing which cannot be reduced without reucing the probability of reaching the goal).

A probabilistic planning problem is considered to be probabilistically interesting if and only if it has all the following structural properties:
\begin{itemize}
	\item there are multiple goal trajectories;
	\item there is at least on pair of distinct goal trajectories, $\tau$ and $\tau$ ', that share a common sequence of outcomes for the first n-1 outcomes, and where $\tau$\textsubscript{n} and $\tau$'\textsubscript{n} are distinct outcomes of the same action; and
	\item there exist two distinct goal trajectories $\tau$ and $\tau$' and outcome o $\in$ $\tau$ and o' $\in$ $\tau$' of two distinct actions a = act(o) and a'= act(o') such that executing a strictly decreases the maximum probability of reaching a state where a' can be executed. 
\end{itemize}

Problems that fail to be \emph{probabilistically interesting} are actually classical planning problems in disguise and for those replanners are more appropriate. A replanner can also perform optimally for probabilistically interesting planning problems whenever the 'most promising' goal trajectory is the correct thing to do. They create several domains to explore the issue of replanning vs. probabilistic planning.

Following existing domains were said to be probabilistically interesting:
\begin{itemize}
	\item Drive
	\item Exploding blocksworld
	\item Pitchcatch
	\item Schedule
	\item Tireworld
\end{itemize}

They conclude by stating that the negative perception of probabilistic planning by the ICAPS community was inaccurate. They state that a synthesis of planning and replanning techniques could make a larger number of probabilistic planning problems pacticably solvable than is currently possible.

\section{Domain description}
% Stukje voor domein
Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thiébauw a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise \cite{little2007probvsreplan}. To validate our planners in a real-world domain we will analyze previous and current domain description for the 'probabilistically interestingness' using this baseline test, adjust them to what we consider as being a real-world domain and test it again. Using these

FF-Replan participated in IPPC-04 (and IPPC-06) solving problems that had been specified in the Probabilstic Planning Domain Description Language (PPDDL) whereas Gourmand has been tested on the set of IPPC-11 problems specified in Relational Dynamic Influence Diagram Language (RDDL)\cite{sanner2008rddl}.

\subsection{Planning problem definition}

@@

\begin{itemize}
	\item \cite{Hoffmann01theff}
	\item \cite{FFReplan}
	\item \cite{teichteil2010incremental}
	\item \cite{yoon2008probabilistic}
	\item \cite{teichteil2012fast}
	\item \cite{bonet2011planning}
	\item \cite{taig2013translation}
	\item \cite{martin2013progressive}
	\item \cite{taig2013conformant}
	\item \cite{2013workshop}
	\item \cite{nebel2013much}
	\item \cite{little2007probvsreplan}
	\item \cite{keller2012prost}
	\item \cite{kolobov2012glutton}
	\item \cite{sanner2008rddl}
\end{itemize}
